A formal approach but practical approach in train regulation

### 2025-06-09 paper/main.tex
typo

\begin{document}
%
\title{A formal approach but practical approach in train regulation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Guillaume Bonfante \and Martin Vassor  \and Lucas Villaume}
%
\authorrunning{G. Bonfante et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Université de Lorraine -- CNRS -- INRIA -- LORIA}
%
\maketitle
\todo{Je serai d'avis de mettre Lucas en 1er auteur, car (i) il est le contributeur principal, et (ii) Il y a un best paper award pour étudiants, mais il faut que l'étudiant soit 1er auteur}
%
\begin{abstract}
	% Contexte
	Trains networks are critical system which failure may lead to numerous fatalities, in case of crashes, or important loss, if trains are not properly routed. 
	% Problème
	In this paper, our goal is to formally verify the correctness of train routes. More precisely, we verify the absence of deadlocks, the termination, and the absence of crashes.
	% Approche
	To address this question, we model train systems in TLA+. Our model include trains, as well as switches and traffic lights. Both switches and traffic lights are controlled by a regulator upon train events. We provide trains and the regulator lists of event, which characterise the train scheduling, which is then checked using TLA+'s model checker.
	% Resultats
	Our contributions are threefold: first, we provide a TLA+ specification which can be adapted to various train networks and schedules; second, we report tests we ran on the model on a non-trivial network, composed of 3 trains, 8 blocks and 5 switches; finally we show how to sequentially compose two schedules and to verify the result.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

@@

\begin{wrapfigure}[6]{r}{0.3\textwidth}
\hspace{-10mm}
 \begin{minipage}{0.3\textwidth}
        \centering
        \vspace{-24mm}
\includegraphics[height=50mm]{ZoomAffichage.png}
    \end{minipage}
\end{wrapfigure}

>>>>

\begin{document}
%
\title{A formal approach but practical approach in train regulation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Villaume \and Guillaume Bonfante \and Martin Vassor  }
%
\authorrunning{G. Bonfante et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Université de Lorraine -- CNRS -- INRIA -- LORIA}
%
\maketitle
%
\begin{abstract}
	% Contexte
	Trains networks are critical system which failure may lead to numerous fatalities, in case of crashes, or important loss, if trains are not properly routed. 
	% Problème
	In this paper, our goal is to formally verify the correctness of train routes. More precisely, we verify the absence of deadlocks, the termination, and the absence of crashes.
	% Approche
	To address this question, we model train systems in TLA+. Our model include trains, as well as switches and traffic lights. Both switches and traffic lights are controlled by a regulator upon train events. We provide trains and the regulator lists of event, which characterise the train scheduling, which is then checked using TLA+'s model checker.
	% Resultats
	Our contributions are threefold: first, we provide a TLA+ specification which can be adapted to various train networks and schedules; second, we report tests we ran on the model on a non-trivial network, composed of 3 trains, 8 blocks and 5 switches; finally we show how to sequentially compose two schedules and to verify the result.

\todo{Validé par GB}
\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

@@

\begin{wrapfigure}[7]{r}{0.3\textwidth}
\hspace{-10mm}
 \begin{minipage}{0.3\textwidth}
        \centering
        \vspace{-24mm}
\includegraphics[height=50mm]{ZoomAffichage.png}
    \end{minipage}
\end{wrapfigure}
